Effects of CHILDREN's programs

### 2020-02-22 paper.Rnw
completed first stargazer table

@@

\documentclass[12pt, a4paper]{article}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage[hidelinks]{hyperref}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
\usepackage[onehalfspacing]{setspace}
\usepackage[left = 72 pt, right = 72 pt]{geometry}

@@

<<LoadingPackages, include=FALSE>>=
library(knitr)
library(xtable)
library(dplyr)
@

@@

<<echo=FALSE, results='asis'>>=
library(stargazer)
lm1_selfworth = readRDS("./ANALYSIS/Tables/lm1_selfworth.Rds")
lm2_selfworth = readRDS("./ANALYSIS/Tables/lm2_selfworth.Rds")
lm3_selfworth = readRDS("./ANALYSIS/Tables/lm3_selfworth.Rds")
lm4_selfworth = readRDS("./ANALYSIS/Tables/lm4_selfworth.Rds")
# table1_selfworth <- 
stargazer(lm1_selfworth,
                    lm2_selfworth,
                    lm3_selfworth,
                    lm4_selfworth,
          title = "Regression Results",
          order = c('Constant', 'treatEF'),
          omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
                   'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
                   'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
                   'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
                   'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
                   'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
                   'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
                   'dummy_2018', 'id'
                  ),
          add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
                           c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
          align = TRUE)
# row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")
# colnames(tableDispSumm) <- c("$Corr(X_t, X_{t-1})$", "$\\sigma(X)$", "$\\frac{\\sigma(X)}{\\sigma(Y)}$", "$\\frac{\\sigma(X)}{\\sigma(GDP)}$")
# tableDispSumm <- xtable(tableDispSumm, caption = "Productivity dispersion: Summary statistics", digits = 3, align = "crccc")
# print(tableDispSumm, sanitize.text.function = function(x) {x}, caption.placement = "top")
@

>>>>

% rotate tables in knitr
% https://stackoverflow.com/questions/21840878/rotate-a-table-from-r-markdown-in-pdf
% in particular stargazer tables
% https://stackoverflow.com/questions/31169845/rotate-stargazer-table-in-knitr/34292292#34292292

@@

\documentclass[12pt, a4paper]{article}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage[hidelinks]{hyperref}
\usepackage{rotating}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
\usepackage[onehalfspacing]{setspace}
\usepackage[left = 72 pt, right = 72 pt]{geometry}

@@

<<LoadingPackages, include=FALSE>>=
library(knitr)
library(xtable)
library(dplyr)
library(stargazer)
@

@@

<<echo=FALSE, results='asis', message=FALSE>>=
lm1_selfworth = readRDS("./ANALYSIS/Tables/lm1_selfworth.Rds")
lm2_selfworth = readRDS("./ANALYSIS/Tables/lm2_selfworth.Rds")
lm3_selfworth = readRDS("./ANALYSIS/Tables/lm3_selfworth.Rds")
lm4_selfworth = readRDS("./ANALYSIS/Tables/lm4_selfworth.Rds")

table1_selfworth <- stargazer(lm1_selfworth,
                    lm2_selfworth,
                    lm3_selfworth,
                    lm4_selfworth,
          title = "Regression Results",
          order = c('Constant', 'treatEF'),
          omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
                   'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
                   'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
                   'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
                   'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
                   'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
                   'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
                   'dummy_2018', 'id'
                  ),
          add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
                           c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
          align = TRUE,
          float.env = "sidewaystable")
# row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")
# colnames(tableDispSumm) <- c("$Corr(X_t, X_{t-1})$", "$\\sigma(X)$", "$\\frac{\\sigma(X)}{\\sigma(Y)}$", "$\\frac{\\sigma(X)}{\\sigma(GDP)}$")
# tableDispSumm <- xtable(tableDispSumm, caption = "Productivity dispersion: Summary statistics", digits = 3, align = "crccc")
# print(tableDispSumm, sanitize.text.function = function(x) {x}, caption.placement = "top")
@

### 2020-02-22 paper.tex
completed first stargazer table

\usepackage{alltt}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage[hidelinks]{hyperref}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
\usepackage[onehalfspacing]{setspace}
\usepackage[left = 72 pt, right = 72 pt]{geometry}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'cowplot' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(`\_inherit`, env, NULL): object 'GeomCustomAnn' not found}}\end{kframe}

@@

\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# \\\#\# Please cite as:}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\#\ \ Hlavac, Marek (2018). stargazer: Well-Formatted Regression and Summary Statistics Tables.}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\#\ \ R package version 5.2.2. https://CRAN.R-project.org/package=stargazer}}\end{kframe}
% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sat, Feb 22, 2020 - 8:34:59 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

>>>>

\usepackage{alltt}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage[hidelinks]{hyperref}
\usepackage{rotating}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
\usepackage[onehalfspacing]{setspace}
\usepackage[left = 72 pt, right = 72 pt]{geometry}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sa, Feb 22, 2020 - 21:10:01
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}
